New paper template

### 2024-06-06 manuscript/Manuscript.qmd
MS: abstract edit
more info about Platynereis
multiple manuscript edits

@@

Test of git show.

@@

*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]

@@

We would like to thank the Jekely lab for the R project template (<https://github.com/JekelyLab/new_paper_template>) we used to write this paper. This work was funded by ...

@@

library(readxl)
library(tinytable)

#read data
resources_table <- readxl::read_xls("../analysis/data/Key_resource_table.xls")

@@

| Col1 | Col2 | Col3 | Col4 | Col5 |
|------|------|------|------|------|
| a    | b    | c    | d    | e    |
| d    |      |      |      |      |

>>>>

Here is our abstract. We discovered that medaka fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).

@@

Test of git show. And another test.

@@

*Platynereis dumerilii* is a marine annelid... [@ozpolat2021]. It is also the coolest model organism. It lives in shallow sea on seagrass. Ischia is a good campling location.

@@

We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](<https://github.com/JekelyLab/new_paper_template>) we used to write this paper. This work was funded by some funding agency.
We would like to thank all the Platynereis that gave their lives for science.

@@

library(readxl)
library(tinytable)
library(readxl)

# read data
resources_table <- readxl::read_xls("../analysis/data/Key_resource_table.xls")

@@

| Col1 | Col2 | Col3 | Col4 | Col5 |
|------|------|------|------|------|
| a    | b    | c    | d    | e    |
| d    |      |      |      |      |
| v    | n    | f    |      | f    |
